Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-05 02_Paper/paper.tex
Predictive analytics

By considering the lack of literature, our goal is to decrease this gap in the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation. To do so, we need to select the right testing platform. This platform should represent real industrial applications and be able to handle a certain level of complexity. In our work, we applied a case-based research approach \cite{yin2017case} to answer the research question \AP{what research question?}. One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.

>>>>

By considering the lack of literature, our goal is to decrease this gap in the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation. To do so, we need to select the right testing platform. It has to have a clear production process, complete access to sensor data, and flexible enough to reprogram the process if necessary 
In our work, we applied a case-based research approach \cite{yin2017case} to answer the research question \AP{what research question?}. One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.
